---
title: "Pain Discrimination and Learning: Linear Mixed Models"
author: "Fabrice Hubschmid"
date: "2024-01-16"
output: html_document
---

### Set-Up

```{r setup, echo=FALSE}
suppressMessages(suppressWarnings(library(ggplot2)))
suppressMessages(suppressWarnings(library(ggeffects)))
suppressMessages(suppressWarnings(library(GGally)))
suppressMessages(suppressWarnings(library(lme4)))
suppressMessages(suppressWarnings(library(boot)))
suppressMessages(suppressWarnings(library(lattice)))
suppressMessages(suppressWarnings(library(lmerTest)))
suppressMessages(suppressWarnings(library(effects)))
suppressMessages(suppressWarnings(library(car)))
suppressMessages(suppressWarnings(library(tictoc)))
suppressMessages(suppressWarnings(library(tidyverse)))
suppressMessages(suppressWarnings(library(emmeans)))
suppressMessages(suppressWarnings(library(broom.mixed)))
suppressMessages(suppressWarnings(library(multcomp)))
getwd()
```

### Data import

```{r, echo=FALSE}
data <- read.csv("PDL_data_discrimination_all.csv", header = T, sep = ";")
data$subj_idx<-factor(data$subj_idx)
data$stim<-factor(data$stim)
data$reward<-factor(data$reward)
data$reward<-relevel(data$reward,ref="NR")
data$response<-factor(data$response)
levels(data$reward)<-c("no reward", "contingent", "non-contingent")
levels(data$stim)<-c("+0°C", "+0.2°C", "+0.4°C")
```

```{r}
str(data)
```
### Collumns:  
01 -> subj_idx (unique subject ID)  
02 -> participant_log (initial subject name before renaming to HDDM convention)  
03 -> session_number_log(what session it was (only 1))  
04 -> trial_number  
05 -> condition_log (logged temperature pulse condition)  
06 -> stim (renamed pulse conditions (control 0°C, difficult 0.2°C, easy 0.4°C))  
07 -> split_by (used for the RL models)  
08 -> reward (trial allocation to reward condition)  
09 -> answer_log (answered logged by the computer)  
10 -> choice_code (coding of stimulus choice to 1 = yes / 0 = no)  
11 -> response (coding of discrimination accuracy to 1 = correct / 0 = false)  
12 -> rt (reaction time)  
13 -> contingency (participant allocation to reward group)  
14 -> reinforcement (wether there was reinforcement in each trial)  
15 -> feedback (reward feedback to 1 = received / 0 = no reward received)  
16 -> q.init (used for the initialization of Q values in the RL models)  
17 -> cumulative_reward (cummulation of monetary rewards during session)  
18 -> predeterminedlist (use of a predetermined reward schedule (see non-contingent))  
19 -> prop (proportion of accurate discrimination averaged over pulse and reward (only used for plotting))

## Mixed Logistic Regression: Detection Accuracy

Models a random intercept only with no interaction assumed

```{r}
tic()
MLR1.intercept <- glmer(response ~ stim + reward + (1|subj_idx), data = data, family = binomial(link='logit'))
toc()
MLR1.intercept%>%summary()
```

### Confidence intervals of the fixed effects:

```{r}
tic()
confint(MLR1.intercept)
toc()
```

### Odds ratios associated with the fixed effects:

```{r}
tidy(MLR1.intercept,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```

### Contrast comparisons averaged over pulse condition

```{r}
(MLR1.intercept_post_hoc_rewards <- pairs(emmeans(MLR1.intercept, ~ reward,type="response"))%>%test())
```

### Contrast comparisons averaged over reward conditions

```{r}
(MLR1.intercept_post_hoc_pulses <- pairs(emmeans(MLR1.intercept, ~ stim,type="response"))%>%test())
```

## Linear Mixed Model: Reaction Times

Models a random intercept only with no interaction assumed

```{r}
tic()
LMM2.intercept <- lmer(rt~ stim + reward + (1| subj_idx), data = data)
summary(LMM2.intercept)
toc()
```

### Confidence intervals of the fixed effects:

```{r}
tic()
confint(LMM2.intercept)
toc()
```
### Contrast comparisons averaged over pulse condition

```{r}
suppressMessages(
(LMM2.intercept_post_hoc_rewards <- pairs(emmeans(LMM2.intercept, ~ reward,type="rt"))%>%test())
)
```

### Contrast comparisons averaged over reward conditions

```{r}
suppressMessages(
(MLR1.intercept_post_hoc_pulses <- pairs(emmeans(MLR1.intercept, ~ stim,type="response"))%>%test())
)
```

End...